Parallel Deduplication with Batch Scheduling for Collocated Virtual Machine Backup in the Cloud

### 2014-01-07 batchdedup/scheduling.tex

There is another disadvantage with a single-round scheduling. 
During backup period, new data modification requests can lead a inconsistency between data signature 
read previously and actual data on the disk.
% This works well if all of the
% data being backed up are only copies, e.g. a separate backup system which data
% is sent to over the network. 
%However, in our case we are backing up the
%live virtual disks, thus such single round backup presents several problems
%in our synchronous approach.
In order to preserve a consistent view of VM images, we employ
the Copy-on-Write (CoW) technique to protect the dirty segments against incoming disk writes during 
the backup period~\cite{VMare2013}. 
The cost of CoW is a factor of the data size, the write rate, and duration of CoW protection.
Previous studies have shown that as much as 8\% or even more of total disk capacity may have to be 
reserved for CoW~\cite{EMCIncrementalDataChanges}.
Prolonging the backup time of individual VM backup  caused by skewed VM size distribution
and single-round operation synchronization significantly increases COW overhead.
%The second problem is that a single round backup brings the highest cost of CoW
%because of the workload in stage 1a is imbalanced,
%causing machines with small VMs to wait while CoW protection is turned on.
%Thus we must minimize the duration that a given VM is undergoing CoW protection.

>>>>

There is another disadvantage with a single-round scheduling. 
During backup period, new data modification requests can lead a inconsistency between data signature 
read previously and actual data on the disk.
% This works well if all of the
% data being backed up are only copies, e.g. a separate backup system which data
% is sent to over the network.

%However, in our case we are backing up the
%live virtual disks, thus such single round backup presents several problems
%in our synchronous approach.
In order to preserve a consistent view of VM images, we employ
the Copy-on-Write (CoW) technique to protect the dirty segments against incoming disk writes during 
the backup period~\cite{VMare2013}. 
The cost of CoW is a factor of the data size, the write rate, and duration of CoW protection.
Previous studies have shown that as much as 8\% or even more of total disk capacity may have to be 
reserved for CoW~\cite{EMCIncrementalDataChanges}.
Prolonging the backup time of individual VM backup  caused by skewed VM size distribution
and single-round operation synchronization significantly increases COW overhead.
%The second problem is that a single round backup brings the highest cost of CoW
%because of the workload in stage 1a is imbalanced,
%causing machines with small VMs to wait while CoW protection is turned on.
%Thus we must minimize the duration that a given VM is undergoing CoW protection.

To determine how evenly distributed VM sizes are, we obtained statistical data
for 22 Aliyun clusters. The clusters in our dataset all have a very long tail distribution,
Though local minima exist in the histogram and the range of VM sizes varies. Other production clusters
may have different distributions, but our findings justify our architecture for a multi-round algorithm.
A representative histogram for one of the clusters is shown in Fig.~\ref{fig:hist-1}.

\begin{figure}[ht]
  \centering
  \begin{tikzpicture}
      \begin{axis}[
              ybar interval,
      ]
          \addplot+[hist={bins=10}] table[y=AY41G] {figures/cluster_distributions.txt};
      \end{axis}
  \end{tikzpicture}
  \caption{Histogram of average data sizes for a real cluster. TODO:reformat graph, I just wanted to get the data into the paper}
  \label{fig:hist-1}
\end{figure}
